Do motif roles provide unique information about species risk of extinction?

### 2021-06-29 manuscript/motifs_vs_degree.tex
Updates from Overleaf

        Network average persistence of consumers naturally decreases with increasing level of disturbance of basal resources (Table S1, \emph{Appendix SA}). Network size and connectance also affect persistence, but to a much smaller extent (Figure S1, \emph{Appendix SA}). Persistences generally decrease when networks are more connected, but the effect of network size varies depending on level of disturbance: at low disturbance, small and highly-connected webs show the lowest persistence, whereas at high disturbance, large and highly connected webs show the lowest persistence (Fig. S2, \emph{Appendix SA}).

>>>>

         Network size and connectance affected persistence, but to a much smaller extent than increasing disturbance to basal resources (Figure S1, Table S1, \emph{Appendix SA}). Persistences generally decrease when networks are more connected, but the effect of network size varies depending on level of disturbance. At low disturbance, small and highly-connected webs show the lowest persistence, whereas at high disturbance, large and highly connected webs show the lowest persistence (Fig. S2, \emph{Appendix SA}).
